\section*{Reviewer 4}

\paragraph{R4.1} We have added a deeper comparison with the algorithm in Sleep Hunter in the experimental part of the paper. That is, making their algorithms applied to the raw sensor data of our smartwatch to prove the advantages of SLEEPGUARD and the fact that the improvement of its accuracy is not only due to changes in equipment. The results are now given in Section 4.2.3. See also R1.1. Thanks for the comments.

\paragraph{R4.2} Because each person's sleep habits are very different, even the same person's probability of appearing three hand positions in different sleeping environments and physical conditions are different. Therefore, as shown in Figure 20, we only show a statistically averaged result in the paper, that is, counting the occurrence of three hand positions separately in the user's 14-day sleep data in order to evaluate the performance of the algorithm detection effectively. Please see also R5.1. Please see our response to R1.2
\vspace{-2mm}

\paragraph{R4.3} The occurrence of micro-body movements of each person is random, which may be related to factors such as the physical condition of the person, and it is not a problem of concern to the user, so we do not regard the number of occurrences of micro-body movements as the focus of attention. And as shown in Figure 21, we counted and evaluated the accuracy of SLEEPGUARD's detection of all micro-body movements for each user for 14 days. Please see also R5.2. Thanks for the feedback.
\vspace{-2mm}
\paragraph{R4.4} Table 9 shows the average sleep quality score for each participant for 14 days. And we have added additional information and analysis to Table 9, which makes our statement of results more relevant. This information is now given in Section 4.2.4. Please see also R5.3. Thanks for your valuable comment.

